--- 
title: "我的笔记模板"
# subtitle: "Lecture title"
author:
- affiliation: Dongbei University of Finance & Economics
  name: Studennt. Li Junjie
date: '`r Sys.Date()`'
output:
  bookdown::html_document2:
    # code_folding: hide
    highlight: pygments
    # highlight: zenburn
    # highlight: haddock
    theme: darkly
    # theme: cerulean
    df_print: paged	
    number_sections: true
    keep_md: no
    keep_tex: no
    toc: yes
    toc_depth: 5
    toc_float:
      collapsed: no
      smooth_scroll: yes
    # css: styles.css
# bibliography: [book.bib, packages.bib]
# biblio-style: apalike
link-citations: yes
sansfont: Times New Roman
always_allow_html: yes
urlcolor: "red"
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
abstract: |
    本章介绍 R 语言编程与数据可视化基础，对比了 base、 lattice 和 ggplot2 包的图形语法，重点介绍了 ggplot2 包的图形语法介绍 R 语言编程与数据可视化基础，对比了 base、 lattice 和 ggplot2 包的图形语法，重点介绍了 ggplot2 包的图形语法
    
    源代码下载 Github 网址： <https://github.com/EasyChart/Beautiful-Visualization-with-R>
---

# 加载经常用的R包

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      cache = FALSE,
                      fig.show = "hold",
                      fig.align = "center",
                      tidy = FALSE)
                      # class.source = "bg-warning")
```

```{r,echo=FALSE}
library(bubblyr)
# bubblyr::bubbly(theme = "sweet")
bubblyr::bubbly(theme = "rstudio")
```

```{js, echo=FALSE}
$('.title').css('color', 'red')
$('.title').css('font-family', 'Times New Roman')
```

```{css, echo=FALSE}
* {
    # font-size: 17px !important;
    font-family: "Times New Roman" !important;
    color: rgb(199 237	204)
}
::selection {
   # background: rgb(135 206 255);
}
```

```{r,warning=FALSE,message=FALSE}
library(pacman)
# 读数据
p_load(readxl,writexl,data.table,openxlsx,haven,rvest)
```

```{r,warning=FALSE,message=FALSE}
# 数据探索
p_load(tidyverse,DT,skimr,DataExplorer,explore,vtable,stringr,kableExtra,lubridate)
```

```{r,eval=FALSE,warning=FALSE,message=FALSE}
# 模型
p_load(grf,glmnet,caret,tidytext,fpp2,forecast,car,tseries,hdm,tidymodels,broom)
```

```{r,eval=FALSE,warning=FALSE,message=FALSE}
# 可视化
p_load(patchwork,ggrepel,ggcorrplot,gghighlight,ggthemes,shiny)
```

```{r,eval=TRUE,warning=FALSE,message=FALSE}
# 其它常用包
p_load(magrittr,listviewer,devtools,here,janitor,reticulate,jsonlite)
```

# 前言

This is a _sample_ book written in *Markdown*[@R-base]. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$^[This is a footnote.]

The *bookdown* package can be installed from CRAN or Github:

## 技巧

- [@R-base]
- $a^2 + b^2 = c^2$
- \^[This is a footnote.]
- \# Preface {-}
- fig.dim = c(6,4)表示fig.width = 6和fig.height = 4
- out.width = '80％'表示页面宽度的80％
- fig.cap：图形标题
- ```` ```{r}``` ````
- \` r  x  \`
- 同一代码块并排放置多个图形，可以将`r text_spec("fig.show='hold'",color = "red")`选项与`r text_spec('"out.width"',color = "red")`选项一起使用
- `knitr::include_graphics()`函数
- 使用`*number_sections*`选项将节编号添加到标题

## 代码

```{r,collapse=TRUE}
1 + 1
mtcars
```

```{r ,fig.cap="a simple plot"}
iris %>% ggplot(aes(Sepal.Length,Sepal.Width,col = Species)) +
  geom_point() +
  geom_smooth() +
  ggthemes::theme_economist() +
  theme(text = element_text(family = enfont))
```

# Reference
















