--- 
title: "对ggplot2包想说的话"
# subtitle: "Lecture title"
author:
- affiliation: Dongbei University of Finance & Economics
  name: Studennt. Li Junjie
date: '`r Sys.Date()`'
output:
  bookdown::html_document2:
    # code_folding: hide
    highlight: pygments
    # highlight: zenburn
    # highlight: haddock
    theme: darkly
    # theme: cerulean
    df_print: paged	
    number_sections: true
    keep_md: no
    keep_tex: no
    toc: yes
    toc_depth: 5
    toc_float:
      collapsed: no
      smooth_scroll: yes
    # css: styles.css
# bibliography: [book.bib, packages.bib]
# biblio-style: apalike
link-citations: yes
sansfont: Times New Roman
always_allow_html: yes
urlcolor: "red"
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
abstract: |
    ggplot2本身就很强大，简简单单几行代码就可以生成漂亮的图片，加上ggplot2系列扩展包和强大的社区，学好ggplot2，大部分的绘图基本不在话下，难在快速找到自己需要的信息和处理加工，画图简单，画好看的图难。本教程主要汇总ggplot2重要但容易被忽略的知识点。
---

# `r emo::ji("smile")`加载经常用的R包`r emo::ji("smile")`

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      cache = FALSE,
                      fig.show = "hold",
                      fig.align = "center",
                      tidy = FALSE)
                      # class.source = "bg-warning")
```

```{r,echo=FALSE}
library(bubblyr)
bubblyr::bubbly(theme = "sweet")
# bubblyr::bubbly(theme = "rladies")
```

```{js, echo=FALSE}
$('.title').css('color', 'red')
$('.title').css('font-family', 'Times New Roman')
```

```{css, echo=FALSE}
* {
    # font-size: 17px !important;
    font-family: "Times New Roman" !important;
    # color: rgb(199 237	204)
}
::selection {
   # background: rgb(135 206 255);
}
```

```{r,warning=FALSE,message=FALSE}
library(pacman)
# 读数据
p_load(readxl,writexl,data.table,openxlsx,haven,rvest)
```

```{r,warning=FALSE,message=FALSE}
# 数据探索
p_load(tidyverse,DT,skimr,DataExplorer,explore,vtable,stringr,kableExtra,lubridate)
```

```{r,eval=FALSE,warning=FALSE,message=FALSE}
# 模型
p_load(grf,glmnet,caret,tidytext,fpp2,forecast,car,tseries,hdm,tidymodels,broom)
```

```{r,eval=FALSE,warning=FALSE,message=FALSE}
# 可视化
p_load(patchwork,ggrepel,ggcorrplot,gghighlight,ggthemes,shiny)
```

```{r,eval=TRUE,warning=FALSE,message=FALSE}
# 其它常用包
p_load(magrittr,listviewer,devtools,here,janitor,reticulate,jsonlite)
p_load(tidyquant)
```

# `r emo::ji("smile")`Number_format函数`r emo::ji("smile")`

```{r}
ga_claims <- 
  "GAICLAIMS" %>% 
  tq_get(get = "economic.data", 
         from = "1999-01-01") %>% 
  rename(claims = price) 
ga_claims
```

```{r}
ga_claims %>%
  mutate(year = year(date),
         month =  month(date, label = T, abbr  = T)) %>% 
  group_by(year,month) %>% 
  filter(n() >= 4) %>% 
  summarise(avg_claims = mean(claims)) %>% 
  mutate(
    avg_claims_labels = scales::number_format(
      accuracy = 1,
      scale = 1 / 1000,
      suffix = "k",
      big.mark = ","
    )(avg_claims)) %>% 
  ggplot(aes(
    x = month,
    y = year,
    fill = avg_claims,
    label = avg_claims_labels
  )) +
  geom_tile(color = "white", size = .8, aes(height = 1)) +
  mytheme

```

# `r emo::ji("smile")`geom_segment绘制箭头图`r emo::ji("smile")`

```{r}
df2 <- expand.grid(
  lineend = c('round', 'butt', 'square'),
  linejoin = c('round', 'mitre', 'bevel'),
  stringsAsFactors = FALSE
)
df2 <- data.frame(df2, y = 1:9)

df2
```

```{r}
ggplot(df2, aes(
  x = 1,
  y = y,
  xend = 2,
  yend = y,
  label = paste(lineend, linejoin)
)) +
  geom_segment(
    lineend = df2$lineend,
    linejoin = df2$linejoin,
    size = 3,
    arrow = arrow(length = unit(0.3, "inches"))
  ) +
  geom_text(hjust = 'outside', nudge_x = -0.2,family = "Times New Roman") +
  xlim(0.5, 2) +
  mytheme

```

# `r emo::ji("smile")`统计变换Stats`r emo::ji("smile")`

## `r emo::ji("flowers")`stat_ecdf`r emo::ji("flowers")`

```{r}
df <- data.frame(
  x = c(rnorm(100, 0, 3), rnorm(100, 0, 10)),
  g = gl(2, 100)
)

# Don't go to positive/negative infinity
ggplot(df, aes(x)) + stat_ecdf(geom = "step", pad = FALSE) + mytheme
```

## `r emo::ji("flowers")`stat_ellipse`r emo::ji("flowers")`

```{r}
ggplot(faithful, aes(waiting, eruptions)) +
  geom_point() +
  stat_ellipse() +
  mytheme
```

```{r}
ggplot(faithful, aes(waiting, eruptions, color = eruptions > 3)) +
  geom_point() +
  stat_ellipse() +
  mytheme
```

```{r}
ggplot(faithful, aes(waiting, eruptions, color = eruptions > 3)) +
  geom_point() +
  stat_ellipse(type = "norm", linetype = 2) +
  stat_ellipse(type = "t") +
  mytheme
```

```{r}
ggplot(faithful, aes(waiting, eruptions, fill = eruptions > 3)) +
  stat_ellipse(geom = "polygon") +
  mytheme
```

## `r emo::ji("flowers")`geom_function():如何在一张图上添加分布图`r emo::ji("flowers")`

```{r}
data.frame(x = rnorm(10000)) %>% 
  ggplot(aes(x)) +
  geom_density() +
  geom_function(fun = dnorm,col = "red") +
  geom_vline(xintercept = 0,linetype = 2,col = "orange") +
  mytheme
```

```{r}
dnorm(0)
ggplot() + xlim(-5,5) + geom_function(fun = dnorm) + mytheme
```

```{r}
ggplot() + xlim(-5,5) + geom_function(fun = dnorm, args = list(mean = 2,sd = .5)) + mytheme
```

```{r}
ggplot() + xlim(-5,5) + stat_function(fun = dnorm,args = list(mean = 2,sd = 0.5),
                                      geom = "point") +
  mytheme

ggplot() + xlim(-5,5) + stat_function(fun = dnorm,args = list(mean = 2,sd = 0.5),
                                      geom = "line") +
  mytheme
```

```{r}
ggplot() +
  xlim(-5,5) +
  geom_function(aes(colour = "normal"), fun = dnorm) +
  geom_function(aes(colour = "t, df = 1"), fun = dt, args = list(df = 1)) +
  mytheme
```

```{r}
ggplot() + xlim(-5,5) + geom_function(fun = function(x) 0.5*exp(-abs(x))) + mytheme
```

## `r emo::ji("flowers")`stat_summary`r emo::ji("flowers")`

```{r}
mtcars %>% 
  ggplot(aes(cyl,mpg)) +
  geom_point() -> d
```

```{r}
d + mytheme
```

```{r}
d + stat_summary(fun.data = "mean_cl_boot",col = "red",size = 2) + mytheme
```

```{r}
mtcars %>% 
  ggplot(aes(mpg,cyl)) +
  geom_point() +
  stat_summary(fun.data = "mean_cl_boot",col = "red",size = 2) +
  mytheme
```

```{r}
d + stat_summary(fun = "median", colour = "red", size = 2, geom = "point") + mytheme
```

```{r}
d + stat_summary(fun = "mean",geom = "point",size = 2,col = "red") + mytheme
```

```{r}
d + aes(colour = factor(vs)) + stat_summary(fun = mean, geom="line") + mytheme
```

# `r emo::ji("smile")`Aesthetics`r emo::ji("smile")`

```{r}
p <- ggplot(nlme::Oxboys, aes(Occasion, height,fill = Occasion)) + geom_boxplot()
p + mytheme
p + geom_line(aes(group = Subject), colour = "blue") + mytheme +
  geom_point(col = "orange")
```

The `linetype` aesthetic can be specified with either an `integer` (0-6), a name (0 = `blank`, 1 = `solid`, 2 = `dashed`, 3 = `dotted`, 4 = `dotdash`, 5 = `longdash`, 6 = `twodash`), a mapping to a **discrete variable**, or a string of an even number (up to eight) of hexadecimal digits which give the lengths in consecutive positions in the string. See examples for a hex string demonstration.

```{r}
df2 <- data.frame(x = 1:5 , y = 1:25, z = 1:25)
p <- ggplot(df2, aes(x, y,group = factor(z)))
p + geom_point(aes(shape = z), size = 4) +
  scale_shape_identity() +
  mytheme
```

# `r emo::ji("smile")`Scales`r emo::ji("smile")`

```{r,fig.width=8}
# Show a list of available shapes
df_shapes <- data.frame(shape = 0:24)
ggplot(df_shapes, aes(0, 0, shape = shape)) +
  geom_point(aes(shape = shape), size = 5, fill = 'red') +
  scale_shape_identity() +
  facet_wrap(~shape) +
  guides(x = guide_axis(angle = 90)) +
  mytheme
```

# `r emo::ji("smile")`Guides: axes and legends`r emo::ji("smile")`

```{r}
df <- expand.grid(X1 = 1:10, X2 = 1:10)
df$value <- df$X1 * df$X2

p1 <- ggplot(df, aes(X1, X2)) + geom_tile(aes(fill = value))
p1 + mytheme
```

```{r}
p1 + geom_point(aes(size = value)) + mytheme
```

```{r}
# title text styles via element_text
p1 + guides(fill =
  guide_legend(
    title.theme = element_text(
      size = 15,
      face = "italic",
      colour = "red",
      angle = 0
    )
  )
)
```

# `r emo::ji("smile")`Labels`r emo::ji("smile")`

```{r}
p1 <- ggplot(mtcars, aes(x = mpg, y = wt)) + geom_point()
p1 + mytheme
```

```{r}
# You can assign different labellers to variables:
p1 + facet_grid(
  vs + am ~ gear,
  labeller = labeller(vs = label_both, am = label_value)
) + mytheme
```

```{r}
# Or whole margins:
p1 + facet_grid(
  vs + am ~ gear,
  labeller = labeller(.rows = label_both, .cols = label_value)
) + mytheme
```

```{r}
rainbow2 <- matrix(hcl(seq(0, 360, length.out = 10), 80, 70), nrow = 1)
rainbow2
df <- tibble(x = 1:10, y = 1)
df
ggplot(df, aes(x, y)) +
  annotation_raster(rainbow2, -Inf, Inf, -Inf, Inf) +
  geom_point(col = "pink",size = 20) +
  scale_x_continuous(breaks = 1:10) +
  scale_y_continuous(breaks = seq(0.8,1.2,0.2),limits = c(0.8,1.2),
                     expand = c(0,0)) +
  annotate(geom = "text",
           x = 1:10,
           y = 1,
           label = c("会","当","凌","绝","顶","一","览","众" ,"山","小"),
           col = "red",
           size = 5) +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank()) +
  labs(x = NULL,
       y = NULL) 

```

# `r emo::ji("smile")`其他资源`r emo::ji("smile")`

- 笔记
- OneNote笔记
- ggplot2官网



